---
title: "Identify Missing Metadata"
---

## Problem
Don't you hate it when you're asked to work on a database project and after you say "Sure, no problem. Where's the documentation?" and you get this blank look? If so, this article helps demonstrate how to use this package to document an existing database. We'll start by connecting to the database and document its existing schema. Then we'll identify missing metadata that should probably be added to improve the project documentation. 

```{r import-labraries}
library(usaceki)
library(keyring)
library(DBI)
library(ROracle)
library(dplyr)
library(stringr)
library(rdflib)
```

## EQRI
The USACE Engineering Quality Risk Indicator (EQRI) application allows staff to record and track engineering quality indicators for reporting and analysis. 

## Extract RDMS Schema Metadata

```{r}
# Connect to Database
qri_connection <- get_qri_connection(set_key = FALSE)

# Get list of tables
tables <- get_tables(qri_connection)

# Get a list of tables with df of column metadata
table_info <- get_table_info(qri_connection, tables)

# Get primary keys
pk_info <- get_pk(qri_connection)

# Get foreign keys
fk_info <- get_fk(qri_connection)

# Get table comments
table_comments <- get_table_comments(qri_connection)

# Get column comments
column_comments <- get_column_comments(qri_connection)
```


## Map RDMS Schema to RDF
```{r}
# Create an empty RDF graph
g <- rdf()

# Define namespace bindings (used at serialization time)
ns <- c(
  ex = "http://usace.gov/rf-dm#",
  owl = "http://www.w3.org/2002/07/owl#",
  rdfs = "http://www.w3.org/2000/01/rdf-schema#",
  rdf = "http://www.w3.org/1999/02/22-rdf-syntax-ns#",
  xsd = "http://www.w3.org/2001/XMLSchema#",
  skos = "http://www.w3.org/2004/02/skos/core#"
)

# Map all tables (table_info is a named list where names are table names)
for (tbl in names(table_info)) {
  g <- map_table_to_rdf(
    g,
    tbl,
    table_info[[tbl]],
    pk_info,
    tab_comments,
    col_comments
  )
}

# Map foreign keys (assuming fk_info is available)
g <- map_foreign_keys_to_rdf(g, fk_info)
```


```{r map-tables}

```

```{r}

```